### 2008-09-16 trunk/Latex/H2Preview/H2PrevPreproc.tex
Added diagrams, response to reviewers, and made minor corrections to start of FF section

It follows from (\ref{proj_prop}) and the fact that a feedforward controller does not alter $T_{w\rightarrow z}$, that $\nrm{T_{\tiny{\ma{w\\ \eta}\rightarrow z}}}_2$ is minimised by choosing the feedforward controller which minimises $\nrm{T_{\eta \rightarrow z}}_2$. Given these observations, we may neglect the influence of $w$ in the design process.

@@

The problem considered in this section is illustrated in Figure \ref{fig:DistRejSysFF}. By modifying (\ref{eqn:P}), it follows that the appropriate generalised plant is given by:
\aln{
P_{FF}&\shorteq\ma{\arr{cc|c:c}{
A_g&B_{1gr}C_{d1}&0&B_{2g}\\
0&A_d&B_{d}&0\\\hline
C_{1g} &D_{11gr}C_{d1} &0&D_{12}\\ \hdashline
0&C_{d2}&D_r&0
}}\label{eqn:PFF}\\
&=\ssmod{A}{B_1}{B_2}{C_1}{C_2}{D_{11}}{D_{12}}{D_{21}}{0}
.}

>>>>

%It follows from (\ref{proj_prop}) and the fact that a feedforward controller does not alter $T_{w\rightarrow z}$, that $\nrm{T_{[w'\,\, \eta']'\rightarrow z}}_2$ is minimised by choosing the feedforward controller which minimises $\nrm{T_{\eta \rightarrow z}}_2$.

Potentially, one could formulate a feedforward problem by removing the measurement signal $y$ from the configuration in Figure~\ref{fig:DistRejSys}. However, if we recall that 
\als{
\nrm{T_{{[\eta'\,\,w']'}\rightarrow z}}^2_2 =
\nrm{T_{w\rightarrow z}}^2_2+
\nrm{T_{\eta\rightarrow z}}^2_2,}
and that a feedforward controller does not alter $T_{w\rightarrow z}$, then it follows that $\nrm{T_{[w'\,\, \eta']'\rightarrow z}}_2$ is minimised by choosing the feedforward controller which minimises $\nrm{T_{\eta \rightarrow z}}_2$.  Given these observations, we may neglect the influence of $w$ in the design process.

@@

The problem considered in this section is illustrated in Figure \ref{fig:DistRejSysFF}. Such a configuration is apparently a special case of Figure~\ref{fig:DistRejSys}, and so it is tempting to try to tackle this problem by using the above general theory with $y$ set to zero (by setting $D_{21gw}$, $D_{21gr}$, $C_{2g}$ and $D_{22g}$ to zero) and with $w$ removed. Unfortunately, such an approach does not succeed because assumption (A5) is violated. We will now derive a solution to this problem.

By modifying (\ref{eqn:P}), it follows that the appropriate generalised plant is given by:
\aln{
P_{FF}&\shorteq\ma{\arr{cc|c:c}{
A_g&B_{1gr}C_{d1}&0&B_{2g}\\
0&A_d&B_{d}&0\\\hline
C_{1g} &D_{11gr}C_{d1} &0&D_{12}\\ \hdashline
0&C_{d2}&D_r&0
}}\label{eqn:PFF}\\
&=\ssmod{A}{B_1}{B_2}{C_1}{C_2}{D_{11}}{D_{12}}{D_{21}}{0}
.}
